Brownian Dynein Model

### 2015-07-24 latex/derivation.tex
Simplify angular solutions more. Add all solutions at bottom of document. Next step: Find way to actually solve, if possible.

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big) (L_{s}\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(L_{s}\sin(\Theta_{mr}-\pi))
\end{multline}

\section{Solution for $\dot{\Theta_{ml}}$}

@@

\section{Solution for $\dot{\Theta_{bl}}$}

@@

>>>>

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big( \mn L_{t}\cos(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{Y}_{t }  + \dot{Y}_{mr} - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(L_{t}\sin(\Theta_{br}-\pi) \dot{\Theta}_{br} + \dot{X}_{t } + \dot{X}_{mr} - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}

\section{Solution for $\dot{\Theta}_{ml}$}

@@

\begin{multline}
\dot{\Theta}_{ml} =
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

\section{Solution for $\dot{\Theta}_{bl}$}

@@

\begin{multline}
\dot{\Theta}_{bl} = \\
\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

\clearpage

\section{All Angular Velocity Solutions}

\begin{multline}
\dot{\Theta}_{mr} =
\frac{1}{L_{s}} \Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{ymr} - R_{ybr} \Big)(\cos(\Theta_{mr}-\pi))\\
  - \frac{1}{L_{s}}\Big(\dot{Y}_{br} + \dot{Y}_{t } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xmr} - R_{xbr} \Big)(\sin(\Theta_{mr}-\pi))
\end{multline}

\begin{multline}
\dot{\Theta}_{ml} =
\Big(\frac{1}{L_s}\cos(\Theta_{ml})\Big) \Big(\dot{Y}_{mr} + \dot{X}_{br} + \dot{Y}_{ml}
- \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yt} - R_{ymr} - R_{ybr} \Big) \\
- \Big(\frac{1}{L_s}\sin(\Theta_{ml})\Big)\Big(\dot{X}_{mr} + \dot{X}_{br} + \dot{X}_{ml}
- \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}

\begin{multline}
\dot{\Theta}_{bl} = \\
\hspace*{-1.5cm}\frac{1}{L_t}\cos(\Theta_{bl})\Big(\dot{Y}_{bl} + \dot{Y}_{t } + \dot{Y}_{mr} + \dot{Y}_{br}
- \frac{1}{\gamma}F_{yml} - \frac{1}{\gamma}F_{yt } - \frac{1}{\gamma}F_{ymr} - \frac{1}{\gamma}F_{ybr} - R_{yml} - R_{yt} - R_{ymr} - R_{ybr} \Big)\\
- \hspace*{-1.5cm}\frac{1}{L_t}\sin(\Theta_{bl})\Big(\dot{X}_{bl} + \dot{X}_{t } + \dot{X}_{mr} + \dot{X}_{br}
 - \frac{1}{\gamma}F_{xml} - \frac{1}{\gamma}F_{xt } - \frac{1}{\gamma}F_{xmr} - \frac{1}{\gamma}F_{xbr} - R_{xml} - R_{xt } - R_{xmr} - R_{xbr} \Big)
\end{multline}
